Introduction

### 2015-07-19 dissertation/problems.tex
reformulate a bit
some evaluation problems

@@

\begin{problem}
Adapt programming languages to deal with dynamic RDF data containing a
mix of terminological and assertional information.
\end{problem}

>>>>

\begin{problem}
Evaluation methodologies are not founded on sound statistics.
\end{problem}

\begin{problem}
Few laws of the Semantic Web information space can reasonably be
expected to have validity far beyond the present.
\end{problem}

\begin{problem}
Evaluation methodologies has no foundation in philosophy of science.
\end{problem}

@@

\begin{problem}
Current programming paradigm deals poorly with dynamic RDF data
containing a mix of terminological and assertional information.
\end{problem}
